Fragile Families - Epigenome wide association study

### 2021-10-26 Reports/FFEWAS.Rmd
results for oct 25 FF meeting

```{r load libraries, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(minfi)
library(limma)
library(matrixStats)
library(MASS)
#library(sva) --> current problem with png package, lib.png.16 https://stackoverflow.com/questions/47424249/unable-to-install-the-package-png-on-r-possible-conflict-with-anaconda/50935430
#library(Hmisc)
#library( missMethyl )
library(ggplot2)
library(qqman)
library(tidyr)
library(dplyr)
library(ggupset)
library(purrr)
library(broom.mixed)
library(future)
library(furrr)
library(tibble)
library(kableExtra)
library(cowplot)
library(matrixStats)
library(lme4)
library(lmerTest)
library(ggpubr)
data.dir="/scratch/bfoxman_root/bfoxman/blostein/FragileFamilies/Files/"
limma.out.dir<-file.path(data.dir, 'CreatedData', 'limmaModels')
outputdir<-"/scratch/bfoxman_root/bfoxman/blostein/FragileFamilies/Output"
```

@@

AllModelsdf<-AllModels %>% bind_rows(.id='ModelType')%>%mutate('Model'=gsub('.*_', '', ModelType), 'Age'=gsub('_.*', '', ModelType))

@@

```{r teen beta vs child beta draw graph, figure.height=16, , fig.cap='Correlation between effect estimates from the three different epigenome wide linear models in children vs in teens for A) all CpGs and B) significant CpGs only'}
plot_grid(all_beta, sig_beta, ncol=2, labels=c('A', 'B'), vjust = 0.8)
```
```{r save beta comparison}
png(file.path(outputdir, 'BetaChildvsTeen.png'), width=1300, height=800)
plot_grid(all_beta_pres+theme(text=element_text(size=16)), sig_beta_pres+theme(text=element_text(size=16)), ncol=1, labels=c('A', 'B'), vjust = 0.8)
dev.off()
```

>>>>

```{r load libraries, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(minfi)
library(limma)
library(matrixStats)
library(MASS)
#library(sva) --> current problem with png package, lib.png.16 https://stackoverflow.com/questions/47424249/unable-to-install-the-package-png-on-r-possible-conflict-with-anaconda/50935430
#library(Hmisc)
#library( missMethyl )
library(ggplot2)
library(qqman)
library(tidyr)
library(dplyr)
library(ggupset)
library(purrr)
library(broom.mixed)
library(future)
library(furrr)
library(tibble)
library(kableExtra)
library(cowplot)
library(matrixStats)
library(lme4)
library(lmerTest)
library(ggpubr)
data.dir="/scratch/bfoxman_root/bfoxman/blostein/FragileFamilies/Files/"
limma.out.dir<-file.path(datadir, 'CreatedData', 'limmaModels')
outputdir<-"/scratch/bfoxman_root/bfoxman/blostein/FragileFamilies/Output"
```

@@

@@

```{r teen beta vs child beta draw graph, figure.height=16, , fig.cap='Correlation between effect estimates from the three different epigenome wide linear models in children vs in teens for A) all CpGs and B) significant CpGs only'}
plot_grid(all_beta, sig_beta, ncol=2, labels=c('A', 'B'), vjust = 0.8)
```

```{r save beta comparison}
png(file.path(outputdir, 'BetaChildvsTeen.png'), width=1300, height=800)
plot_grid(all_beta_pres+theme(text=element_text(size=16)), sig_beta_pres+theme(text=element_text(size=16)), ncol=1, labels=c('A', 'B'), vjust = 0.8)
dev.off()
```
